The ChEMBL database as Linked Open Data

### 2012-04-15 article.tex
Added text on the :has_role :drug

\begin{table*}
\caption{Prefixes and their matching namespaces used in this paper.} \label{namespaces}
\begin{tabular}{ll}
\hline
\multicolumn{2}{l}{\textbf{Common Vocabularies}} \\
bibo    & Bibliography Ontology~\cite{Giasson2011} \\
        & http://purl.org/ontology/bibo/ \\
cheminf & Chemical Information Ontology~\cite{Hastings2011} \\
        & http://semanticscience.org/resource/ \\
cito    & Citation Typing Ontology~\cite{Shotton2010} \\
        & http://purl.org/spar/cito/ \\
pro     & PRotein Ontology~\cite{Sidhu2006} \\
        & http://purl.obolibrary.org/obo/ \\

@@

For drug discovery, the drugs themselves are the main topic of study.
ChEMBL contains many different drug types, mostly small molecules,
but also peptides, proteins, oligosaccharides, oligonucleotides, and
even antibodies. All compounds are represented as classes, following
the design of the CHEMINF ontology. The compound typing is expressed
by subclassing other classes. For example, proteins subclass the
Protein concept from the PRotein Ontology (PR\_000000001), small
molecules subclass the Chemical Entity concept from the CHEMINF
ontology (CHEMINF\_000000), and oligosaccharides and oligonucleotides
subclass their respective matches in the CHEBI ontology (CHEBI\_50699
and CHEBI\_7754). For each drug compound the name and synonyms are
provided as labels. When InChI and InChIKeys are available for a drug, then these are
provided via the CHEMINF formalism (here abbreviated):

>>>>

\begin{table*}
\caption{Prefixes and their matching namespaces used in this paper.} \label{namespaces}
\begin{tabular}{ll}
\hline
\multicolumn{2}{l}{\textbf{Common Vocabularies}} \\
bibo    & Bibliography Ontology~\cite{Giasson2011} \\
        & http://purl.org/ontology/bibo/ \\
chebi   & Chemical Entities of Biological Interest~\cite{DeMatos2010} \\
        & http://purl.org/obo/owl/CHEBI\# \\
cheminf & Chemical Information Ontology~\cite{Hastings2011} \\
        & http://semanticscience.org/resource/ \\
cito    & Citation Typing Ontology~\cite{Shotton2010} \\
        & http://purl.org/spar/cito/ \\
obo / pro & OBO \& PRotein Ontology~\cite{Sidhu2006} \\
          & http://purl.obolibrary.org/obo/ \\

@@

For drug discovery, the drugs themselves are the main topic of study.
ChEMBL contains many different drug types, mostly small molecules,
but also peptides, proteins, antibodies, oligosaccharides, oligonucleotides, and
even cells. All compounds are represented as classes, following
the design of the CHEMINF ontology. These entities do not have a common
superclass in common, but can easily be identified as having the 
the role of being a drug. This is triplified using the OBO and ChEBI
ontologies:

\begin{footnotesize}
\begin{verbatim}
mol:m4 obo:has_role chebi:CHEBI_23888 .
\end{verbatim}
\end{footnotesize}

The entity typing is expressed
by subclassing other classes. For example, proteins subclass the
Protein concept from the PRotein Ontology (PR\_000000001), small
molecules subclass the Chemical Entity concept from the CHEMINF
ontology (CHEMINF\_000000), and oligosaccharides and oligonucleotides
subclass their respective matches in the CHEBI ontology (CHEBI\_50699
and CHEBI\_7754). For each drug compound the name and synonyms are
provided as labels. When InChI and InChIKeys are available for a drug, then these are
provided via the CHEMINF formalism (here abbreviated):
